Model LF

### 2023-03-14 paper version Hamid test.Rmd
Commit

@@

@@

>>>>

```{r}
plot(window(wage_ds_01 - wage_ds_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

```{r}
plot(window((pconk_ds_01 - pconk_ds_bs1), start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 1", ylim= c(-300,300));
lines(window((ik_01 - ik_bs1), start= 2014), col= "green", lwd=2);
legend("top", legend=c("Consumption","Investments"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

```{r}
plot(window(wage_ds_02 - wage_ds_bs2, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 2");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

```{r}
plot(window((pconk_ds_02 - pconk_ds_bs2), start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 2", ylim= c(-50,150));
lines(window((ik_02 - ik_bs2), start= 2014), col= "green", lwd=2);
legend("top", legend=c("Consumption","Investments"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

## Scenario 3
```{r}
plot(window(wage_ds_03 - wage_ds_bs3, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 3");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

```{r}
plot(window((pconk_ds_03 - pconk_ds_bs3), start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 3", ylim= c(-50,150));
lines(window((ik_03 - ik_bs3), start= 2014), col= "green", lwd=2);
legend("top", legend=c("Consumption","Investments"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```
